### 2016-08-26 Chapters/ContinuumSolvationModels.tex
Update notations

\begin{itemize}
    \item why and how continuum solvation models
    \item derivation of \acs{IEF}-\acs{PCM}, importance of Green's
      functions.
    \item \ac{BEM} and wavelet \acs{BEM} I think it's necessary to
      mention also ddCOSMO and ddPCM as alternative strategies (put a
      reference)
    \item variational formulation (no derivations, just mention the
      relevant literature)
\end{itemize}

@@

\section{Boundary integral equations}\label{sec:BIE}

\subsection{Transmission problem}
We assume Euclidean space $\mathbb{R}^3$ to be partitioned into two
subdomains $\Omegai$ and $\Omegae$ sharing a boundary $\Gamma$.
We further assume that $\Omegai$ is a closed domain, entirely contained inside $\Omegae$.
The transmission problem is posed as follows:
\todo[inline]{Some consideration on suitable functional spaces and the metric thereof.}
\begin{subequations}\label{eq:transmission}
\begin{align}
  \Li u &= f_\mathrm{i} \,\, \text{in}\,\, \Omegai \label{eq:internal} \\
  \Le u &= f_\mathrm{e} \,\, \text{in}\,\, \Omegae \label{eq:external} \\
  [u] &= \ue - \ui = g_\mathrm{D} \,\, \text{on}\,\, \Gamma
  \label{eq:trace-jump} \\
[\partial_L u] &= \partiale u - \partiali u = g_\mathrm{N} \,\,
\text{on}\,\, \Gamma \label{eq:conormal-jump} \\
|u| &\leq C \|x \|^{-1} \,\,\text{for}\,\,\| x \|\rightarrow\infty
\label{eq:radiation}
\end{align}
\end{subequations}
where the jump conditions (eqs. \eqref{eq:trace-jump} and
\eqref{eq:conormal-jump}) are given in terms of Dirichlet and Neumann
data for the solution $u$. The jump conditions are expressed in terms of
trace operators for the solution $u$ and its conormal derivative. For
notational simplicity, will use the symbols $\partiale$ and $\partiali$
for the latter and only give it in explicit form when needed. Please
refer to the book by \citeauthor{Sauter2011} for further details. The
fundamental solutions, or Green's functions, for the elliptic
differential operators $\Li$ and $\Le$ will be denoted by $\Gi$ and
$\Ge$, respectively.

\subsection{Boundary integral operators}
We introduce the relevant boundary integral operators for the abovementioned
transmission problem. They are three of the four components of the Calder\'on projector.
For $v \in L^2(\Gamma)$, $x, y \in \Gamma$:\footnote{We can assume a less restrictive functional space, \ie a Sobolev space of fractional order.}
\begin{equation}
\begin{aligned}
(\bi{S}_\star v)(x) &= \int_\Gamma G_\star(x, y)v(y)\diff y \\
(\bi{D}_\star v)(x) &= \int_\Gamma \partial_{L_\star,y}G_\star(x, y)v(y)\diff y \\
(\bi{D}^\dagger_\star v)(x) &= \int_\Gamma \partial_{L_\star,x}G_\star(x, y)v(y)\diff y \\
\end{aligned}
\end{equation}
where $\star$ is a placeholder for the $\mathrm{i}$ or $\mathrm{e}$ subscript.

\begin{lemma}[Properties of the boundary integral operators]
  The integral operators introduced above enjoy the following
  properties~\autocite{Hsiao2008, Sauter2011}:
  \begin{enumerate}
      \item on $L^2(\Gamma)$ $\bi{S}_\star$ is self-adjoint,
        $\bi{D}^\dagger_\star$ is the adjoint operator of
        $\bi{D}_\star$.
      \item The commutation relations:
        \begin{alignat}{2}
          \bi{D}_\star\bi{S}_\star = \bi{S}_\star\bi{D}^\dagger_\star, \quad&
          \bi{S}_\star\bi{D}_\star = \bi{D}^\dagger_\star\bi{S}_\star
        \end{alignat}
        hold
      \item The operators:
        \begin{subequations}
          \begin{align}
   \bi{S}_\star &: H^{-\frac{1}{2}}(\Gamma) \rightarrow H^{\frac{1}{2}}(\Gamma) \\
   \bi{D}_\star &: H^{\frac{1}{2}}(\Gamma) \rightarrow H^{\frac{1}{2}}(\Gamma) \\
   \bi{D}^\dagger_\star &: H^{-\frac{1}{2}}(\Gamma) \rightarrow H^{-\frac{1}{2}}(\Gamma)
          \end{align}
        \end{subequations}
      \item The operator $\bi{S}_\star$ is coervice and admits a
        continuous inverse in the aforementioned Sobolev spaces.
      \item The operators $\lambda - \bi{D}_\star$ and $\lambda -
        \bi{D}^\dagger_\star$ with $\lambda \in (-2\pi, +\infty)$
        admit a continuous inverse in the aforementioned
        Sobolev spaces.
  \end{enumerate}
\end{lemma}

@@

\pagebreak
\section{IEFPCM}\label{sec:IEF}

@@

%%%% CASE 0

\subsection{Case 0: sources in a vacuum cavity inside a dielectric}

\begin{figure}[h!]
  \centering
  \includegraphics[width=.65\textwidth]{case0}
  \caption{Vacuum Cavity in dielectric with permittivity $\diel_\mathrm{e}>1$.
  Source charge density $\rho_\mathrm{i}$ inside the cavity
  ($\diel_\mathrm{i}=1$). \textcolor{red}{Regular IEF}}
  \label{fig:case0}
\end{figure}

This is the regular IEF as derived in:~\autocite{Cances1998}
\begin{subequations}
\begin{align}
  \nabla^2 u &= \rhoi \,\, \text{in}\,\, \Omegai \\
  \Le u &= 0 \,\, \text{in}\,\, \Omegae \\
  [u] &= \ue - \ui = 0 \,\, \text{on}\,\, \Gamma \\
[\partial_L u] &= \partiale u - \partiali u = 0 \,\,
\text{on}\,\, \Gamma \\
|u| &\leq C \|x \|^{-1} \,\,\text{for}\,\,\| x \|\rightarrow\infty
\end{align}
\end{subequations}

@@

\begin{enumerate}
  \item Add Eqs. \eqref{eq:second} and \eqref{eq:third}:
    \begin{equation}
    \bi{S}_\mathrm{e}(\partiale \xi + \partiale h) -
    \bi{D}_\mathrm{e}(\xi_\mathrm{e} + h_\mathrm{e})
    = -\frac{1}{2}(\xi_\mathrm{e} + h_\mathrm{e})
    \end{equation}
  \item Exploit Eqs. \eqref{eq:fourth} and \eqref{eq:fifth} to
    eliminate the external traces and conormal derivatives:
    \begin{equation}
      \bi{S}_\mathrm{e}(\partiali \xi) + \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)\xi_\mathrm{i} =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Introduce the integral representation of
    $\xi_\mathrm{i}$:
    \begin{equation}
      \bi{S}_\mathrm{e}(\partiali \xi) + \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}\sigma =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Reorganize Eq. \eqref{eq:first}, using the commutation
    relation and the integral representation of $\xi_\mathrm{i}$:
    \begin{equation}
    \partiali \xi = \left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)\sigma
    \end{equation}
    such that:
    \begin{equation}
      \left[ \bi{S}_\mathrm{e}\left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)
      +
      \left(\frac{1}{2} - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
      \right]\sigma =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Employ the Dirichlet-to-Neumann (DtN) map to simplify
    the RHS. The DtN map is derived by applying Eq. \eqref{eq:stat3} to
    the Newton potential:
    \begin{equation}
      \phi(x) = (\bi{N}\rhoi)(x) = \int_{\mathbb{R}^3}\Gi\rhoi(y)\diff y
      = \left.h(x)\right|_{\Omegai}
    \end{equation}
    which is equal, in $\Omegai$, to the auxiliary potential $h(x)$.
    With this definition one has:
    \begin{equation}
      \frac{1}{2}\phi_\mathrm{i} =
      \bi{S}_\mathrm{i}(\partiali \phi) -
      \bi{D}_\mathrm{i}(\phi_\mathrm{i}) + \int_{\Omegai}\Gi\rhoi(y)\diff y
      =
      \bi{S}_\mathrm{i}(\partiali \phi) -
      \bi{D}_\mathrm{i}(\phi_\mathrm{i}) + \phi_\mathrm{i}
    \end{equation}
    eventually leading to the DtN map:
    \begin{equation}\label{eq:regular-DtN}
      \left(\frac{1}{2} - \bi{D}_\mathrm{i}\right)\phi_\mathrm{i}
      +\bi{S}_\mathrm{i}(\partiali \phi) = 0
    \end{equation}
  \item Having identified $\phi_\mathrm{i} \equiv h_\mathrm{i}$
    and $\partiali \phi \equiv \partiali h$ and employing the DtN map,
    Eq.\eqref{eq:regular-DtN}, one obtains the IEF-PCM equation:
    \begin{equation}\label{eq:regular-IEF}
      \left[ \bi{S}_\mathrm{e}\left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)
      +
      \left(\frac{1}{2} - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
      \right]\sigma =
      -\left[\left(\frac{1}{2}-\bi{D}_\mathrm{e}\right)
      -\bi{S}_\mathrm{e}\bi{S}_\mathrm{i}^{-1}
       \left(\frac{1}{2}-\bi{D}_\mathrm{i}\right)
      \right]\phi
    \end{equation}
    where the subscript $\mathrm{i}$ for the Newton potential $\phi$ has
    been dropped, given that it is continuous across the boundary
    $\Gamma$.
\end{enumerate}
The above proves the existence of a representation of the reaction
potential valid \emph{inside} the cavity in terms of an apparent surface
charge density. We do not prove the uniqueness of this solution and
refer the interested reader to the original paper.~\autocite{Cances1998}

In the code, the Green's functions are defined \emph{without} the $4\pi$
factors in the denominator. Instead of $\frac{1}{2}$ as coefficients to
the identity operator, one will then have $2\pi$:
\begin{equation}\label{eq:regular-IEF-2pi}
  \left[ \bi{S}_\mathrm{e}\left(2\pi + \bi{D}^\dagger_\mathrm{i}\right)
  +
  \left(2\pi - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
  \right]\sigma =
  -\left[\left(2\pi-\bi{D}_\mathrm{e}\right)
  -\bi{S}_\mathrm{e}\bi{S}_\mathrm{i}^{-1}
  \left(2\pi-\bi{D}_\mathrm{i}\right)
  \right]\phi
\end{equation}

\paragraph{Isotropic IEF}
From Eq. \eqref{eq:regular-IEF-2pi} we can derive the isotropic IEF,
the DPCM and the CPCM (by letting $\diel\rightarrow\infty$) equations.
For a homogeneous, isotropic dielectric with permittivity $\diel$ the
Green's function outside the cavity is simply given by scaling the one
inside:
\begin{equation}
  \Ge = \frac{1}{\diel|x-y|} = \frac{1}{\diel} \Gi = \frac{1}{|x-y|}
\end{equation}
leading to the boundary integral operators:
\begin{alignat}{2}
  \bi{S}_\mathrm{i} = \diel\bi{S}_\mathrm{e} = \bi{S}, \quad&
  \bi{D}_\mathrm{i} = \bi{D}_\mathrm{e} = \bi{D}
\end{alignat}
Eventually, one has:
\begin{equation}
  \left[ 2\pi \left(\frac{\diel+1}{\diel-1}\right)
  - \bi{D} \right]\bi{S}\sigma
  =
  -\left[2\pi-\bi{D}\right]\phi
\end{equation}

\section[Variational Formulation of Classical Polarizable Models]{
A Unifying View of Classical Polarizable Models within a Variational Formulation}
\label{sec:variational}

Variational functional for implicit models, \acs{PCM} in this case:
\begin{equation}
 U_\mathrm{PCM} = \frac{1}{2}\scalprod{\sigma}{\PCM\sigma} + \scalprod{\esp}{\sigma}
\end{equation}

Variational functional for explicit models, could be MMpol or PE or FQ:
\begin{equation}
  U_\mathrm{MM} = \frac{1}{2}\kappa\MM\kappa + \kappa\zeta
\end{equation}

The PCM equations will be written in the ``complete basis'' meaning that
we will introduce the usual boundary-element method (BEM) discretization
at the very end of the derivation. In other words, we will be working
with the exact integral equation and not with its discretized
counterpart. As a consequence, the apparent surface charge $\sigma$ and
the electrostatic potential $\esp$ will have a \emph{continuous}
dependence on a ``cavity surface'' index $\vect{s}$. Whenever a
charge-potential product is present it is then to be interpreted as the
\emph{surface integral}, i.e. the scalar product in the suitable,
infinite-dimensional vector space on the cavity boundary $\Gamma$. The
following shorthand notation will be adopted:
\begin{equation}
 \sigma\esp = \scalprod{\sigma}{\esp}
\end{equation}

Coupled implicit/explicit polarization energy functional:
\begin{equation}\label{eq:pcm-mm-functional}
  U_\mathrm{pol} =
   \frac{1}{2}\sigma\PCM\sigma + \sigma\esp
 + \frac{1}{2}\kappa\MM\kappa + \kappa\zeta
 + \sigma\bi{X}\kappa
\end{equation}
where one has:
\begin{equation}
  \sigma\MMPCM\kappa = \kappa\MMPCM^\dagger\sigma
\end{equation}
and $\MMPCM$ is the implicit/explicit interaction kernel. This is
charge/dipole or charge/charge interaction kernel for the MMpol and PE models
or the FQ model, respectively.
The global minimum of the convex functional is found by differentiating
it with respect to the variational degrees of freedom, \ie{} the
\acl{ASC} (\acs{ASC}) density $\sigma$ and the classical point
charges/dipoles $\kappa$. This leads to the coupled equations:
\begin{align}
  \PCM\sigma + \esp + \MMPCM\kappa &= 0 \\
  \MM\kappa  + \zeta + \MMPCM^\dagger\sigma &= 0
\end{align}
or in the commonly found matrix form:
\begin{equation}
  \begin{pmatrix}
    \PCM & \MMPCM \\
    \MMPCM^\dagger & \MM
  \end{pmatrix}
  \begin{pmatrix}
   \sigma \\
   \kappa
  \end{pmatrix}
  =
  -
  \begin{pmatrix}
   \esp \\
   \zeta
  \end{pmatrix}
\end{equation}
Finally, let us re-express the equations above in a "supermatrix"
formalism:
\begin{equation}
  U_\mathrm{pol} =
  \frac{1}{2}{}^t\p\V\p + {}^t\p\s
\end{equation}
where:
\begin{alignat}{3}
  \p =
  \begin{pmatrix}
    \sigma \\
    \kappa
  \end{pmatrix},
  \quad&
  \s =
  \begin{pmatrix}
   \esp \\
   \zeta
  \end{pmatrix},
  \quad&
  \V =
  \begin{pmatrix}
    \PCM & \MMPCM \\
    \MMPCM^\dagger & \MM
  \end{pmatrix}
\end{alignat}
and the ${}^t\p$ symbol denotes the transposed supervector $\p$.
The supermatrix form will prove particularly useful in the following
derivations.

\todo[inline]{PUT REFERENCES HERE!!!}
The variational formulation offers a series of advantages.
The classical energy functional:
\begin{equation}
  U_\mathrm{pol} =
   \frac{1}{2}\sigma\PCM\sigma + \sigma\esp
 + \frac{1}{2}\kappa\MM\kappa + \kappa\zeta
 + \sigma\bi{X}\kappa
\end{equation}
renders itself to a straightforward physical interpretation. In the
three bilinear terms, \ie{} the ones mediated by an interaction
operator, we can identify the self-interaction of the classical
polarization with itself, be it purely implicit:
$\frac{1}{2}\sigma\PCM\sigma$, purely explicit
$\frac{1}{2}\kappa\MM\kappa$ or mixed $\sigma\MMPCM\kappa$.
These terms are positive definite and give rise to an unfavorable
contribution, which is counterbalanced by the linear terms. These terms
mediate the interaction between the induced polarization and the
inducing fields: $\esp$ and $\zeta$. While $\esp$ is quite clearly the
\acl{MEP} (\acs{MEP}), $\zeta$ can either be the molecular electric
field (MMpol and PE models) or again the \acs{MEP} (FQ model).
In any case, both will be determined by the quantum mechanical molecular
charge density and can thus be formulated as expectation values of
one-electron operators. Eventually, this achieves the coupling between
the classical -- $\sigma$ and $\kappa$ -- and
the quantum mechanical variational degrees of freedom.

>>>>

\begin{itemize}
    \item why and how continuum solvation models
    \item derivation of \acs{IEF}-\acs{PCM}, importance of Green's
      functions.
    \item \ac{BEM} and wavelet \acs{BEM} I think it's necessary to
      mention also ddCOSMO and ddPCM as alternative strategies
      ~\autocite{Cances2013-jg, Lipparini2013-cy, Lipparini2014-to,
      Lipparini2014-fq, Stamm2016-fv}
    \item variational formulation (no derivations, just mention the
      relevant literature)
\end{itemize}

@@

\section{Continuum Electrostatics as a Boundary Integral Problem}\label{sec:IEF}

We assume Euclidean space $\mathbb{R}^3$ to be partitioned into two
subdomains $\Omegai$ and $\Omegae$ sharing a boundary
$\Gamma\equiv\partial\Omegai$.
We further assume that $\Omegai$ is a closed domain, entirely contained
inside $\Omegae$. The boundary $\Gamma$ is thus a closed surface, \ie~a
closed 2-manifold in $\mathbb{R}^3$.
The transmission problem is posed as follows:
\todo[inline]{Some consideration on suitable functional spaces and the metric thereof.}
\begin{subequations}\label{eq:transmission}
  \begin{align}[left={\empheqlbrace}]
  \Li u &= f_\mathrm{i} \,\, \text{in}\,\, \Omegai \label{eq:internal} \\
  \Le u &= f_\mathrm{e} \,\, \text{in}\,\, \Omegae \label{eq:external} \\
  [u] &= \ue - \ui = g_\mathrm{D} \,\, \text{on}\,\, \Gamma
  \label{eq:trace-jump} \\
[\partial_L u] &= \partiale u - \partiali u = g_\mathrm{N} \,\,
\text{on}\,\, \Gamma \label{eq:conormal-jump} \\
|u| &\leq C \|x \|^{-1} \,\,\text{for}\,\,\| x \|\rightarrow\infty
\label{eq:radiation}
\end{align}
\end{subequations}
where the jump conditions (eqs. \eqref{eq:trace-jump} and
\eqref{eq:conormal-jump}) are given in terms of Dirichlet and Neumann
data for the solution $u$. The jump conditions are expressed in terms of
trace operators for the solution $u$ and its conormal derivative. For
notational simplicity, will use the symbols $\partiale$ and $\partiali$
for the latter and only give it in explicit form when needed.
Further mathematical details and technical results on the definition of
function traces and their use in setting up the proper normal and
conormal derivatives can be found in the excellent book by
\citeauthor{Sauter2011-an}.~\autocite{Sauter2011-an}.
The
fundamental solutions, or Green's functions, for the elliptic
differential operators $\Li$ and $\Le$ will be denoted by $\Gi$ and
$\Ge$, respectively.

We introduce the relevant boundary integral operators for the
abovementioned transmission problem. They are three of the four
components of the Calder\'on projector.
For $v \in L^2(\Gamma)$, $x, y \in \Gamma$:
\footnote{We can assume a less restrictive functional space, \ie a
Sobolev space of fractional order.}
\begin{equation}
\begin{aligned}
(\bi{S}_\star v)(x) &= \int_\Gamma G_\star(x, y)v(y)\diff y \\
(\bi{D}_\star v)(x) &= \int_\Gamma \partial_{L_\star,y}G_\star(x, y)v(y)\diff y \\
(\bi{D}^\dagger_\star v)(x) &= \int_\Gamma \partial_{L_\star,x}G_\star(x, y)v(y)\diff y \\
\end{aligned}
\end{equation}
where $\star$ is a placeholder for the $\mathrm{i}$ or $\mathrm{e}$ subscript.

\begin{lemma}[Properties of the boundary integral operators]
  The integral operators introduced above enjoy the following
  properties~\autocite{Hsiao2008-xb, Sauter2011-an}:
  \begin{enumerate}
      \item on $L^2(\Gamma)$ $\bi{S}_\star$ is self-adjoint,
        $\bi{D}^\dagger_\star$ is the adjoint operator of
        $\bi{D}_\star$.
      \item The commutation relations:
        \begin{alignat}{2}
          \bi{D}_\star\bi{S}_\star = \bi{S}_\star\bi{D}^\dagger_\star, \quad&
          \bi{S}_\star\bi{D}_\star = \bi{D}^\dagger_\star\bi{S}_\star
        \end{alignat}
        hold
      \item The operators:
        \begin{subequations}
          \begin{align}
   \bi{S}_\star &: H^{-\frac{1}{2}}(\Gamma) \rightarrow H^{\frac{1}{2}}(\Gamma) \\
   \bi{D}_\star &: H^{\frac{1}{2}}(\Gamma) \rightarrow H^{\frac{1}{2}}(\Gamma) \\
   \bi{D}^\dagger_\star &: H^{-\frac{1}{2}}(\Gamma) \rightarrow H^{-\frac{1}{2}}(\Gamma)
          \end{align}
        \end{subequations}
      \item The operator $\bi{S}_\star$ is coervice and admits a
        continuous inverse in the aforementioned Sobolev spaces.
      \item The operators $\lambda - \bi{D}_\star$ and $\lambda -
        \bi{D}^\dagger_\star$ with $\lambda \in (-2\pi, +\infty)$
        admit a continuous inverse in the aforementioned
        Sobolev spaces.
  \end{enumerate}
\end{lemma}

@@

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.65\textwidth]{IEF}
  \caption{Vacuum Cavity in dielectric with permittivity $\diel_\mathrm{e}>1$.
  Source charge density $\rho_\mathrm{i}$ inside the cavity
  ($\diel_\mathrm{i}=1$). \textcolor{red}{Regular \acs{IEF}}}
  \label{fig:case0}
\end{figure}

This is the regular \acs{IEF} as derived in:~\autocite{Cances1998-og}
\begin{subequations}
\begin{align}
  \nabla^2 u &= \rhoi \,\, \text{in}\,\, \Omegai \\
  \Le u &= 0 \,\, \text{in}\,\, \Omegae \\
  [u] &= \ue - \ui = 0 \,\, \text{on}\,\, \Gamma \\
[\partial_L u] &= \partiale u - \partiali u = 0 \,\,
\text{on}\,\, \Gamma \\
|u| &\leq C \|x \|^{-1} \,\,\text{for}\,\,\| x \|\rightarrow\infty
\end{align}
\end{subequations}

@@

\begin{enumerate}
  \item Add Eqs. \eqref{eq:second} and \eqref{eq:third}:
    \begin{equation}
    \bi{S}_\mathrm{e}(\partiale \xi + \partiale h) -
    \bi{D}_\mathrm{e}(\xi_\mathrm{e} + h_\mathrm{e})
    = -\frac{1}{2}(\xi_\mathrm{e} + h_\mathrm{e})
    \end{equation}
  \item Exploit Eqs. \eqref{eq:fourth} and \eqref{eq:fifth} to
    eliminate the external traces and conormal derivatives:
    \begin{equation}
      \bi{S}_\mathrm{e}(\partiali \xi) + \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)\xi_\mathrm{i} =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Introduce the integral representation of
    $\xi_\mathrm{i}$:
    \begin{equation}
      \bi{S}_\mathrm{e}(\partiali \xi) + \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}\sigma =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Reorganize Eq. \eqref{eq:first}, using the commutation
    relation and the integral representation of $\xi_\mathrm{i}$:
    \begin{equation}
    \partiali \xi = \left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)\sigma
    \end{equation}
    such that:
    \begin{equation}
      \left[ \bi{S}_\mathrm{e}\left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)
      +
      \left(\frac{1}{2} - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
      \right]\sigma =
      - \bi{S}_\mathrm{e}(\partiali h) - \left(\frac{1}{2} -
      \bi{D}_\mathrm{e}\right)h_\mathrm{i}
    \end{equation}
  \item Employ the \ac{DtN} map to simplify
    the RHS. The \acs{DtN} map is derived by applying Eq. \eqref{eq:stat3} to
    the Newton potential:
    \begin{equation}
      \phi(x) = (\bi{N}\rhoi)(x) = \int_{\mathbb{R}^3}\Gi\rhoi(y)\diff y
      = \left.h(x)\right|_{\Omegai}
    \end{equation}
    which is equal, in $\Omegai$, to the auxiliary potential $h(x)$.
    With this definition one has:
    \begin{equation}
      \frac{1}{2}\phi_\mathrm{i} =
      \bi{S}_\mathrm{i}(\partiali \phi) -
      \bi{D}_\mathrm{i}(\phi_\mathrm{i}) + \int_{\Omegai}\Gi\rhoi(y)\diff y
      =
      \bi{S}_\mathrm{i}(\partiali \phi) -
      \bi{D}_\mathrm{i}(\phi_\mathrm{i}) + \phi_\mathrm{i}
    \end{equation}
    eventually leading to the \acs{DtN} map:
    \begin{equation}\label{eq:regular-DtN}
      \left(\frac{1}{2} - \bi{D}_\mathrm{i}\right)\phi_\mathrm{i}
      +\bi{S}_\mathrm{i}(\partiali \phi) = 0
    \end{equation}
  \item Having identified $\phi_\mathrm{i} \equiv h_\mathrm{i}$
    and $\partiali \phi \equiv \partiali h$ and employing the \acs{DtN} map,
    Eq.\eqref{eq:regular-DtN}, one obtains the \acs{IEF}-\acs{PCM} equation:
    \begin{equation}\label{eq:full-IEF}
      \left[ \bi{S}_\mathrm{e}\left(\frac{1}{2} + \bi{D}^\dagger_\mathrm{i}\right)
      +
      \left(\frac{1}{2} - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
      \right]\sigma =
      -\left[\left(\frac{1}{2}-\bi{D}_\mathrm{e}\right)
      -\bi{S}_\mathrm{e}\bi{S}_\mathrm{i}^{-1}
       \left(\frac{1}{2}-\bi{D}_\mathrm{i}\right)
      \right]\phi
    \end{equation}
    where the subscript $\mathrm{i}$ for the Newton potential $\phi$ has
    been dropped, given that it is continuous across the boundary
    $\Gamma$.
\end{enumerate}
The above proves the existence of a representation of the reaction
potential valid \emph{inside} the cavity in terms of an apparent surface
charge density. We do not prove the uniqueness of this solution and
refer the interested reader to the original
paper.~\autocite{Cances1998-og}

In the code, the Green's functions are defined \emph{without} the $4\pi$
factors in the denominator. Instead of $\frac{1}{2}$ as coefficients to
the identity operator, one will then have $2\pi$:
\begin{equation}\label{eq:full-IEF-2pi}
  \left[ \bi{S}_\mathrm{e}\left(2\pi + \bi{D}^\dagger_\mathrm{i}\right)
  +
  \left(2\pi - \bi{D}_\mathrm{e}\right)\bi{S}_\mathrm{i}
  \right]\sigma =
  -\left[\left(2\pi-\bi{D}_\mathrm{e}\right)
  -\bi{S}_\mathrm{e}\bi{S}_\mathrm{i}^{-1}
  \left(2\pi-\bi{D}_\mathrm{i}\right)
  \right]\phi
\end{equation}

From Eq. \eqref{eq:full-IEF-2pi} we can derive the isotropic
\acs{IEF}, the \acs{DPCM} and the \acs{CPCM} (by letting
$\diel\rightarrow\infty$) equations.
For a homogeneous, isotropic dielectric with permittivity $\diel$ the
Green's function outside the cavity is simply given by scaling the one
inside:
\begin{equation}
  \Ge = \frac{1}{\diel|x-y|} = \frac{1}{\diel} \Gi = \frac{1}{|x-y|}
\end{equation}
leading to the boundary integral operators:
\begin{alignat}{2}
  \bi{S}_\mathrm{i} = \diel\bi{S}_\mathrm{e} = \bi{S}, \quad&
  \bi{D}_\mathrm{i} = \bi{D}_\mathrm{e} = \bi{D}
\end{alignat}
Eventually, one has:
\begin{equation}\label{eq:isotropic-IEF}
  \left[ 2\pi \left(\frac{\diel+1}{\diel-1}\right)
  - \bi{D} \right]\bi{S}\sigma
  =
  -\left[2\pi-\bi{D}\right]\phi
\end{equation}

\section{Detour and Teaser: Weak Formulation of Partial Differential Equations}\label{sec:weak}

From the strong to the weak formulation of \acp{PDE}.\autocite{Ern2004-oo}

\begin{itemize}
  \item Poisson's equation with conductor boundary conditions
        % This is COSMO!
        % This equation makes sense iff \Psi \in \mathcal{C}^2_0(C) (at least)
        % \Psi = 0 \quad \forall \vect{r}\in\partial C
        \begin{equation*}
            \nabla^2\Psi = -4\pi\rho
            % Dirichlet boundary conditions for a conductor
          \quad \Psi \in \mathcolor{ForestGreen}{\mathcal{C}^2_0(C)}
        \end{equation*}
  \item Project onto the space of test functions
        % Project onto the space of test functions
        \begin{equation*}
          \left\{
          \begin{aligned}
            &\text{Seek $\Psi\in\mathcolor{ForestGreen}{V_0}$ such that:}\\
            &(\zeta, \nabla^2\Psi) =
            -4\pi(\zeta, \rho) \quad
            \forall
            \zeta\in\mathcolor{BurntOrange}{\mathcal{C}^\infty_0(C)}
          \end{aligned}
          \right.
        \end{equation*}
  \item Use
    $\eta\nabla^2\gamma = \nabla\cdot(\eta\nabla\gamma) - \nabla\eta\cdot\nabla\gamma$
        % The integral of the first term on the RHS vanishes.
        % It can be shown using Gauss' Theorem and the conductor
        % boundary conditions.
        \begin{equation*}
          \left\{
          \begin{aligned}
            &\text{Seek $\Psi \in \mathcolor{ForestGreen}{H_0^1(C)}$ such that:}\\
            &\mathcolor{Red}{(\nabla\zeta, \nabla\Psi)} =
            \mathcolor{Blue}{-4\pi(\zeta, \rho)} \quad
            \forall \zeta\in \mathcolor{BurntOrange}{H_0^1(C)}
          \end{aligned}
          \right.
        \end{equation*}
\end{itemize}
\begin{equation*}
  \Psi\in \mathcolor{BurntOrange}{H_0^1(C)} = \lbrace f : C \rightarrow
  \mathbb{R} | f \in L^2(C), \nabla f \in L^2(C), f = 0 \forall \vect{s}
  \in\partial C \rbrace
\end{equation*}
\begin{equation}
  \left\{
  \begin{aligned}
    &\text{Seek $\Psi \in V$ such that:}\\
    &\forall \zeta \in V \,\,\,\,\,
    \mathcolor{Red}{a(\zeta, \Psi)} = \mathcolor{Blue}{b(\zeta)}
  \end{aligned}
  \right.
  \label{eq:weak}
\end{equation}

% Hadamard well-posedness definition:
% Problem \eqref{eq:weak} is well-posed if it admits one and only
% one solution and the solution is bounded by the initial data, by
% an a priori estimate (see Ern&Guermond, p.82, Def. 2.1)
\begin{defin}[Well-posedness]\label{def:hadamard}
  The weak problem Eq. \eqref{eq:weak} is \emph{well-posed} if it
  admits one and only one solution and the solution is bounded by
  the initial data by an \emph{a priori} estimate.
\end{defin}
\begin{defin}[Continuity]\label{def:continuity}
  A bilinear form on a normed vector space $V$ is \emph{bounded}, or
  \emph{continuous}, if there is a constant $C$ such that
  $\forall u, v \in V$:
  \[
  a(u, v) \leq C\lVert u\rVert\lVert v\rVert
  \]
\end{defin}
\begin{defin}[Coercivity]\label{def:coercivity}
  A bilinear form on a normed vector space $V$ is \emph{coercive},
  or \emph{elliptic}, if there is a constant $\alpha >0$ such that
  $\forall u \in V$:
  \[
  a(u, u) \geq \alpha\lVert u\rVert^2
  \]
\end{defin}
This implies that no eigenvalue of the linear operator associated
to the bilinear form can be zero, hence that the operator is
invertible!!~\autocite{Ern2004-oo}

% Maybe present connection with Steepest Descent and Conjugate
% Gradient?
% Introduce a suitable vector space, equipped with a norm
% derived from a scalar product.
% The solution belongs to such a vector space, which is
% bigger that in the strong formulation (less constraints on
% the regularity of the solution)
\begin{equation}
  \left\{
  \begin{aligned}
    &\text{Seek $\Psi \in V$ such that:}\\
    &\forall \zeta \in V \,\,\,\,\,
    \mathcolor{Red}{a(\zeta, \Psi)} = \mathcolor{Blue}{b(\zeta)}
  \end{aligned}
  \right.
\end{equation}
\begin{lemma}[Lax--Milgram]
  If the bilinear form $a$ is \emph{continous} and \emph{coercive}
  in $V$, then, for any continuous linear form $b$, Problem~\eqref{eq:weak} is
  \emph{well-posed}.
\end{lemma}
\begin{corollary}[Variational property]
  If the bilinear form is \emph{symmetric} and \emph{positive}
  the unique solution to Problem \eqref{eq:weak} is
  the \emph{unique minimum} on $V$ of the functional:
  \[
  \mathcal{F}(\zeta) = \frac{1}{2}a(\zeta, \zeta) - b(\zeta)
  \]
\end{corollary}

Weak formulation of \acs{BIE}s.\autocite{Hsiao2008-xb}

\section{Numerical Approaches to Boundary Integral Equations}\label{sec:BEM}
